### 2023-08-08 sections/3-methods.tex
added writeup for expanding threshold variant of knn

Given a Cluster $C$, let $c$ be its center and $r$ be its radius.
Let $\delta^0 = f(q, c)$ be the distance from the query to the cluster center.
Let $\delta^1 = \delta^0 + r$ be the distance from the query to the potentially farthest instance in the Cluster.
Let $\delta^2 = max(0, \delta^0 - r)$ be the distance from the query to the potentially closest instance in the Cluster.

\subsubsection{Tree Search}
\label{subsubsec:methods:knn-search:tree-search}

Let $candidates$ be a priority queue sorted by non-decreasing $\delta^1$.
Initialize $candidates$ with the root cluster.
Replace clusters in $candidates$ by their children until $candidates$ has at least $k$ clusters.

Take the $k^{th}$ candidate.
Any cluster with $\delta^2 \leq \delta^2_k$ could contain one of the $k$-nearest neighbors of $q$.
Keep all such clusters in $candidates$ and exclude all other clusters.
Expand search to the children of all $candidates$ so far and repeat until all $candidates$ are leaf clusters.

Sort, as a priority queue, $candidates$ by $\delta^2$ and break ties by $\delta^0$.
Proceed to Leaf Search with these candidates.

>>>>

Given a Cluster $C$, let $c$ be its center and $r$ be its radius.
Let $\delta = f(q, c)$ be the distance from the query to the cluster center.
Let $\delta_{max} = \delta + r$ be the distance from the query to the potentially farthest instance in the Cluster.
Let $\delta_{min} = max(0, \delta - r)$ be the distance from the query to the potentially closest instance in the Cluster.

\subsubsection{Expanding Threshold}
\label{subsubsec:methods:knn-search:expanding-threshold}

Create a priority queue, $candidates$, wherein the top priority candidate is the one with the smallest $\delta_{min}$.
Initialize $candidates$ with the root cluster.
Create a second priority queue, $hits$, wherein the top priority hit is the 
one with the largest $\delta$. This queue starts empty.

While $hits$ has fewer than $k$ clusters or the $\delta$ of the top priority hit is greater 
than the $\delta_{min}$ of the top priority candidate, do the following:
\begin{enumerate}
\item While the top priority candidate isn't a leaf, replace the top priority 
candidate with its children.
\item Remove the top priority candidate from $candidates$ and add all of its 
points to $hits$. 
\item Remove points from $hits$ until $hits$ has $k$ points. 
\end{enumerate}

Extract hits.

\begin{algorithm} % enter the algorithm environment
\caption{Expanding Threshold} % give the algorithm a caption
\label{alg:expanding_threshold} % and a label for \ref{} commands later in the document
\begin{algorithmic}[1] % enter the algorithmic environment
    \REQUIRE $tree$, $query$, $k$
    \STATE $candidates \leftarrow$ priority queue
    \STATE $hits \leftarrow$ priority queue
    \WHILE{$|hits| < k \lor hits.peek().\delta > candidates.peek().\delta_{min}$}
        \WHILE{$!candidates.peek().isLeaf$}
            \STATE $[l, r] \leftarrow candidates.pop().children()$
            \STATE $candidates.push([l, r])$
        \ENDWHILE
        \STATE $leaf \leftarrow candidates.pop()$
        \STATE $hits.push(leaf)$
        \WHILE{$|hits| > k$}
            \STATE $hits.pop()$
        \ENDWHILE
    \ENDWHILE
    \STATE Return $hits$
\end{algorithmic}
\end{algorithm}

\subsubsection{Sieve V1}
\label{subsubsec:methods:knn-search:sieve-v1}
Add explanation of the sieve v1 algorithm.

\subsubsection{Sieve V2}
\label{subsubsec:methods:knn-search:sieve-v2}
Add explanation of the sieve v2 algorithm.

\subsubsection{Repeated Rnn}
\label{subsubsec:methods:knn-search:repeated-rnn}
Add explanation of the repeated rnn algorithm.
